### 2016-05-11 README.Rmd
adjust read badges
this should put the badges onto one line

>>>>

<!-- add a TravisCI badge -->
<!-- Add an appVeyor badge -->
[![Travis-CI Build Status](https://travis-ci.org/tierneyn/visdat.svg?branch=master)](https://travis-ci.org/tierneyn/visdat) [![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/tierneyn/visdat?branch=master&svg=true)](https://ci.appveyor.com/project/tierneyn/visdat)
